Tutorial_2a

### 2024-10-20 Tutorial_2a.Rmd
update tutorials 2a and 2b
update stat_lineribbon in 2a

```{r save-plot-links}
ggsave("Tutorial_2_Bayesian/figures/linkfunctions.png", width = 8, height = 8, dpi = 300)
```

@@

  ggplot(aes(x = period_9, y = value)) +
  stat_lineribbon(show.legend=T) +
  scale_fill_brewer() +
  geom_hline(yintercept=0, linetype="dashed", color = "red") +
  scale_x_continuous(breaks = c(-3:6), labels=c(((-3:6)+9)*40),
                     limits = c(-3,6)) +
  scale_y_continuous(breaks = c(-12,-10,-8,-6,-4,-2,0,2,4,6,8,10,12), limits = c(-12,12)) +
  labs(x = "time bin", y = "cloglog-hazard") +
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(angle=90),
        panel.background = element_rect(fill="white", color="black"),
        legend.position = "top") +
  facet_wrap(~ factor(condition,levels=c("congruent trial 500","congruent trial 1000","congruent trial 1500","incongruent trial 500","incongruent trial 1000","incongruent trial 1500")))

>>>>

```{r save-plot-links, eval=F}
ggsave("Tutorial_2_Bayesian/figures/linkfunctions.png", width = 8, height = 8, dpi = 300)
```

@@

  ggplot(aes(x = period_9, y = value)) +
  stat_lineribbon(point_interval = mean_hdi,.width = c(0.5, 0.8, 0.95),show.legend=T) +
  scale_fill_brewer() +
  geom_hline(yintercept=0, linetype="dashed", color = "red") +
  scale_x_continuous(breaks = c(-3:6), labels=c(((-3:6)+9)*40),
                     limits = c(-3,6)) +
  scale_y_continuous(breaks = c(-12,-10,-8,-6,-4,-2,0,2,4,6,8,10,12), limits = c(-12,12)) +
  labs(x = "time bin endpoint", y = "cloglog-hazard") +
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(angle=90),
        panel.background = element_rect(fill="white", color="black"),
        legend.position = "top") +
  facet_wrap(~ factor(condition,levels=c("congruent trial 500","congruent trial 1000","congruent trial 1500","incongruent trial 500","incongruent trial 1000","incongruent trial 1500")))
